An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-12-31 EconGrowth2.Rnw
No longer using the cesResampleTrianglePlot function.

<<CES_ternary_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelTernaryGraphHeight, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models.">>=
cesResampleTrianglePlot(energyType="Q", nest="all")
@

>>>>

<<CES_ternary_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelTernaryGraphHeight, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models.">>=
cesTriPlotData=loadCESResampleData(energyType="Q", nest="all")
standardTriPlot(data=cesTriPlotData)
@
